---
title: "The World's First PokeApp"
author: "Supro Debnath"
date: '2022-07-28'
---

This shiny app is a demo of all pokemon from Generations 1 through 8. The data can be found through [Kaggle](https://www.kaggle.com/mariotormo/complete-pokemon-dataset-updated-090420). We will be able to look at various metrics that influence a pokemon, as well as allowing for users to subset the data and allow them to select variables that they want to visualize or model. The app provides three supervised learning models that the user can utilize to generate predictions based on whatever variables they select. Everything from the training/testing split to what variables they want to filter on in the raw data is available. The app is meant to demonstrate use of the UI/Server files through various reactive inputs as well as allowing the user to toggle settings they wish to look into or exclude.

## Requirements

To run this app, a few packages must be installed.

- `shiny`: A package that allows for building of interactive web apps.
- `shinythemes`: Selecting a theme for your app.
- `tidyverse`: Collection of R packages that contribute heavily to API interaction and data visualization.
- `knitr`: Provides tools for dynamic reporting in R.
- `dplyr`: Package that provides tools for working with data frames.
- `readr`: Package that allows for rectangular reading of imported data (such as excel files).
- `ggplot2`: Powerful for complex data visualizations.
- `DT`: An R interface package that allows for communication with the JavaScript library `DataTables`.
- `randomForest`: A package that allows for utilization of random forests and functions pertaining to it.
- `caret`: Miscellaneous functions associated with training and testing on regression/classification data.

## Install Packages
```{r}
install.packages(c("shiny", "shinythemes", "tidyverse", "knitr", "dplyr", "readr", "ggplot2", "DT", "randomForest", "caret"))
```

## Libraries
```{r libraries, message=FALSE, warning=FALSE}
library(shiny)
library(shinythemes)
library(tidyverse)
library(knitr)
library(dplyr)
library(readr)
library(ggplot2)
library(DT)
library(randomForest)
library(caret)
```


## Shiny App Code
```{r}
#shiny::runGitHub("ST558-Final-Project", "suproman98") 
```

